Online supplemental material of the article:\\ \vspace{7mm} 'Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming'\\ \vspace{7mm} \normalsize by

### 2020-04-17 Paper/online_supplemental_material/online_material.tex
a few more edits to online material

\usepackage{natbib}
\bibliographystyle{plainnat}
\bibpunct{(}{)}{;}{a}{,}{,}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{float}
\usepackage{soul}
\usepackage{xcolor}
\graphicspath{{./images/}}

@@

For the HSGP model, different models with different number of basis functions and boundary factor have been fitted. The root mean square errors (RMSE) for every one of these models have been computed against the regular GP model, and plotted as a function of the number of basis functions $m$ and boundary factor $c$ in Figure \ref{ch5_fig13_MSE_train_BF_gaydata}-left, for sample data, and in Figure \ref{ch5_fig13_MSE_train_BF_gaydata}-right, for test data. As the boundary factor increases, more basis functions are needed for a accurate approximation, as it was expected.

@@

Figure \ref{ch5_fig15_Posteriors_exII} shows the data-generating GP function, from where the dataset was drawn, and the mean posterior predictive functions of the three models, the regular GP, the HSGP, and the splines, fitted over the dataset. Sample observations are also plotted as circles. For the HSGP model, $m_1=40$ and $m_2=40$ basis functions for each dimension respectively, were used, which lead to a total of 1600 multivariate basis functions. A boundary factor for each dimension $c_1=1.5$ and $c_2=1.5$ were used. For the splines model, 40 knots in each dimension were used.

@@

\begin{figure}
\begin{center}
\begin{tabular}{ c c c}
\includegraphics[scale=0.40, trim = 0mm 33mm 35mm 20mm, clip]{ch5_fig15_truefun_exII.pdf} & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 33mm 35mm 20mm, clip]{ch5_fig15_gpfun_exII.pdf} & \hspace{-5mm}\multirow{-5.5}{*}{ \includegraphics[scale=0.35, trim = 150mm 18mm 0mm 10mm, clip]{ch5_fig15_colorbar_vertical_exII.pdf}}\\ 
\includegraphics[scale=0.40, trim = 0mm 18mm 35mm 20mm, clip]{ch5_fig15_bffun_exII.pdf}  & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 18mm 35mm 20mm, clip]{ch5_fig15_spfun_exII.pdf}
\end{tabular}
\end{center}
\caption{(a) Data-generating function. (b) Mean posterior predictive function of the GP model. (c) Mean posterior predictive function of the HSGP model. (d) Mean posterior predictive function of the splines model. Sample points are plotted as circles}
  \label{ch5_fig15_Posteriors_exII}
\end{figure}

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.36, trim = 1mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorHSGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorSP_exII.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 5mm 0mm 20mm, clip]{ch5_fig16_error_colorbar_exII.pdf}}
\caption{Mean error between the data-generating function and the GP (a), HSGP (b) and splines (c) models. Sample points are plotted as circles.}
  \label{ch5_fig16_errors_exII}
\end{figure}

@@

Figure \ref{ch5_fig18_gpfun_diabetes} shows the mean posterior predictions of probabilities ($p_i$) of the three models, the regular GP, the HSGP and the spline, fitted over the dataset with the 2 input dimensions \textit{Glucose} and \textit{Pregnancy} ($D=2$). The binary observations $y_i$ are also plotted in the plots as colored points. For the HSGP model, $m_1=20$ and $m_2=20$ basis functions for each dimension, respectively, were used, which lead to a total of 400 multivariate basis functions. A boundary factor for each dimension $c_1=4$ and $c_2=4$ were used. For the spline model, 20 knots per dimension were used.
%
\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.37, trim = 5mm 23mm 39mm 20mm, clip]{ch5_fig18_gpfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_bffun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_spfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 4mm 2mm 15mm, clip]{ch5_fig18_legend_diabetes.pdf}}
\caption{(a) Mean posterior predictive functions of the GP model. (b) Mean posterior predictive functions of the HSGP model. (c) Mean posterior predictive functions of the spline (SP) model. Samples observations of suffering (red points) and not suffering (blue points) form the disease are plotted.}
  \label{ch5_fig18_gpfun_diabetes}
\end{figure}

@@

Figure \ref{ch5_fig20_time2D_diabetes} shows the computational times of the different models, regular GP, HSGP and spline, fitted over the dataset with 2, 3 and 4 input dimensions, as a function of the boundary factor $c$ and number of univariate basis functions $m$ and knots. The time of omputation increases significantly with higher dimensions for the HSGP and spline models. In this sense, choosing optimal values for the number of basis functions and boundary factor, looking at the recommendations and diagnosis provided by Figure 6 % \ref{fig6_lscale_vs_J_vs_c}
in the main document, can be essential to avoid a excessive computation time, especially in multivariate input spaces. Serious difficulties with computation time were encountered in building spline models in a 4D input space or even in a 3D input space with more than 10 knots.

@@

\bibliography{references}

>>>>

\usepackage{natbib}
\bibliographystyle{plainnat}
\bibpunct{(}{)}{;}{a}{,}{,}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{float}
\usepackage{soul}
\usepackage{xcolor}
\graphicspath{{../manuscript_v2/images/}}

@@

For the HSGP model, different models with different number of basis functions and boundary factor have been fitted. The root mean square errors (RMSE) for every one of these models have been computed against the regular GP model, and plotted as a function of the number of basis functions $m$ and boundary factor $c$ in Figure \ref{ch5_fig13_MSE_train_BF_gaydata}-left, for sample data, and in Figure \ref{ch5_fig13_MSE_train_BF_gaydata}-right, for test data. As the boundary factor increases, more basis functions are needed for a accurate approximation.

@@

Figure \ref{ch5_fig15_Posteriors_exII} shows the data-generating GP function, from where the dataset was drawn, and the mean posterior predictive functions of the three models, regular GP, HSGP, and splines, fitted over the dataset. Sample observations are also plotted as circles. For the HSGP model, $m_1=40$ and $m_2=40$ basis functions for each dimension respectively, were used, which lead to a total of 1600 multivariate basis functions. A boundary factor for each dimension $c_1=1.5$ and $c_2=1.5$ were used. For the splines model, 40 knots in each dimension were used.

@@

\begin{figure}
\begin{center}
\begin{tabular}{ c c c}
\includegraphics[scale=0.40, trim = 0mm 33mm 35mm 20mm, clip]{ch5_fig15_truefun_exII.pdf} & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 33mm 35mm 20mm, clip]{ch5_fig15_gpfun_exII.pdf} & \hspace{-5mm}\multirow{-5.5}{*}{ \includegraphics[scale=0.35, trim = 150mm 18mm 0mm 10mm, clip]{ch5_fig15_colorbar_vertical_exII.pdf}}\\ 
\includegraphics[scale=0.40, trim = 0mm 18mm 35mm 20mm, clip]{ch5_fig15_bffun_exII.pdf}  & \hspace{-5mm} \includegraphics[scale=0.40, trim = 19mm 18mm 35mm 20mm, clip]{ch5_fig15_spfun_exII.pdf}
\end{tabular}
\end{center}
\caption{(a) Data-generating function. (b) Posterior mean predictive function of the GP model. (c) Posterior mean predictive function of the HSGP model. (d) Posterior mean predictive function of the splines model. Sample points are plotted as circles}
  \label{ch5_fig15_Posteriors_exII}
\end{figure}

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.36, trim = 1mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorHSGP_exII.pdf}}
\subfigure{\includegraphics[scale=0.36, trim = 19mm 18mm 39.2mm 20mm, clip]{ch5_fig16_errorSP_exII.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 5mm 0mm 20mm, clip]{ch5_fig16_error_colorbar_exII.pdf}}
\caption{Error between the data-generating mean function and the posterior mean of the GP (a), HSGP (b) and spline (c) models. Sample points are plotted as circles.}
  \label{ch5_fig16_errors_exII}
\end{figure}

@@

Figure \ref{ch5_fig18_gpfun_diabetes} shows the posterior mean predictions of probabilities ($p_i$) of the three models, regular GP, HSGP and spline, fitted over the dataset with the 2 input dimensions \textit{Glucose} and \textit{Pregnancy} ($D=2$). The binary observations $y_i$ are also plotted in the plots as colored points. For the HSGP model, $m_1=20$ and $m_2=20$ basis functions for each dimension, respectively, were used, which lead to a total of 400 multivariate basis functions. A boundary factor for each dimension $c_1=4$ and $c_2=4$ were used. For the spline model, 20 knots per dimension were used.
%
\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.37, trim = 5mm 23mm 39mm 20mm, clip]{ch5_fig18_gpfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_bffun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.37, trim = 20mm 23mm 39mm 20mm, clip]{ch5_fig18_spfun_diabetes.pdf}}
\subfigure{\includegraphics[scale=0.30, trim = 150mm 4mm 2mm 15mm, clip]{ch5_fig18_legend_diabetes.pdf}}
\caption{(a) Posterior mean predictive functions of the GP model. (b) Posterior mean predictive functions of the HSGP model. (c) Posterior mean predictive functions of the spline (SP) model. Samples observations of suffering (red points) and not suffering (blue points) form the disease are plotted.}
  \label{ch5_fig18_gpfun_diabetes}
\end{figure}

@@

Figure \ref{ch5_fig20_time2D_diabetes} shows the computational times of the different models, regular GP, HSGP and spline, fitted over the dataset with 2, 3 and 4 input dimensions, as a function of the boundary factor $c$ and number of univariate basis functions $m$ and knots. The time of omputation increases significantly with higher dimensions for the HSGP and spline models. In this sense, choosing optimal values for the number of basis functions and boundary factor, looking at the recommendations and diagnosis provided by Figure 6% \ref{fig6_lscale_vs_J_vs_c}
, can be essential to avoid a excessive computation time, especially in multivariate input spaces. Serious difficulties with computation time were encountered in building spline models in a 4D input space or even in a 3D input space with more than 10 knots.

@@

\bibliography{../manuscript_v2/references}
